Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-04-04 docs/ACM/paper.tex
Adding reference to Antao's paper.

\paragraph{On the Implementation of \Taskminer.}
We have implemented all the techniques described in this paper in
LLVM~\cite{Lattner04}.
This decision was motivated by two factors.
First, the possibility to reuse all the infra-structure already
available in LLVM to infer symbolic bounds of integer
expressions~\cite{Mendonca17}.
Second, given the state-of-the-art support that LLVM already provides to the
compilation of OpenMP~\cite{Bertolli14,Martineau16,Samuel16}.

We performed a thorough evaluation on \Taskminer{}'s applicability in real programs. Our test framework is divided in five aspects:

\begin{compactitem}
\item \textsf{Performance}: we run \Taskminer on the BOTS Benchmark and show that the programs annotated by taskminer are sometimes as fast as programs annotated manually, and never slower than their sequential counterparts, thus proving it to be a conservative and useful technique. 
\item \textsf{Optimizations}: we show some optimizations that can be applied to \Taskminer in order to improve performance of the annotated programs.
\item \textsf{Versatility}: we demonstrate \Taskminer's versatility when it is able to find tasks in several different program paradigms.
\item \textsf{Applicability}: we run \Taskminer on larger benchmarks to show the potential of finding task parallelism in big applications.
\item \textsf{Practicality}: here we present \Taskminer's runtime and show that it can be easily used by a programmer to find task parallelism in applications. We evidence \Taskminer's practicality when compared to the method of manually finding parallelism, determining data dependences annotating the program.
\end{compactitem}

%PERFORMANCE
%Here, we show the results for our small benchmarks (toys & bots)
\textbf{\textit{Performance}}.

@@

%OPTIMIZATIONS
%Here, we show the results on two big optimizations: recursion depth and cost model.
%We can use the same benchmarks as above.
\textbf{\textit{Optimizations}}.

@@

%VERSATILITY
%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
\textbf{\textit{Versatility}}.

@@

%APPLICABILITY
%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
\textbf{\textit{Applicability}}.

%PRACTICALITY
%The main objective here is to show that TaskMiner can be easily utilized by a programmer to find tasks in their source code. 
%We'll test TaskMiner's running time.
\textbf{\textit{Practicality}}.

>>>>

We have implemented all the techniques described in this paper in
LLVM~\cite{Lattner04}.
This decision was motivated by two factors.
First, the possibility to reuse all the infra-structure already
available in LLVM to infer symbolic bounds of integer
expressions~\cite{Mendonca17}.
Second, the state-of-the-art support that LLVM already provides to the
compilation of OpenMP~\cite{Antao16,Bertolli14,Martineau16,Samuel16}.
In this section, we evaluate this implementation, focusing on four research
questions:
%
\begin{compactitem}
\item \textsf{[Performance]}: how do our automatically annotated programs
compare against their sequential counterparts, or against manually annotated
versions?
\item \textsf{[Optimizations]}: what is the impact of the cost model
(Section~\ref{sub:profit}) and recursion bounding (Section~\ref{sub:ir}) onto
the programs that we annotate?
\item \textsf{[Versatility]}: how effective is \Taskminer{} in finding
opportunities to annotate general benchmarks?
\item \textsf{[Scalability]}: what is the runtime complexity of our
implementation of \Taskminer?
\end{compactitem}

%PERFORMANCE
%Here, we show the results for our small benchmarks (toys & bots)
\subsection{Performance}.

@@

%OPTIMIZATIONS
%Here, we show the results on two big optimizations: recursion depth and cost model.
%We can use the same benchmarks as above.
\subsection{Optimizations}.

@@

%VERSATILITY
%The goal here is to show that TaskMiner is a versatile tool, capable of finding many types of task parallelism in the code. 
%And the types of tasks that are going to be mined can be easily set, should the programmer ever desires to.
\subsection{Versatility}.

@@

%APPLICABILITY
%We'll show TaskMiner application on larger benchmarks, such as those of spec or those of the LLVM's test-suite.
\subsection{Scalability}.
